### 2015-09-05 fundamentals/examples.tex
spell check
update to examples file, better wording

This section will discuss the creation and results of a few simple fuel cycle
simulations to help illustrate the flexibility of \Cyclus. These examples are
not the limit of \Cyclus' capabilities, which are extended with each new
addition to the ecosystem, as discussed above.  Rather, these simulations are
designed to illustrate that \Cyclus has capabilities matching those of any
recipe-based simulator. Accordingly, many simplifying assumptions have been
made with respect to material compositions, fuel transmutation, among others.
The three fuel cycles examined are:

@@

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{|X|r|X|}
\hline
\textbf{Facility} &\textbf{Parameter} & \textbf{Value}\\
\hline
\textbf{LWR} & type & LWR\\
\Class{cycamore::Reactor} & batches & $3$ [batches/cycle]\\
                  & batch size & $20000$ [kg HM]\\
                  & cycle length & $18$ [months]\\
                  & refuelling time & $2$ [months]\\
                  & requests & recycled MOX (1st preference)\\
                  & requests & enriched UOX (2nd preference)\\
\hline
\textbf{Recycled Fuel Fabrication} & requests & depleted uranium\\
\Class{cycamore::Fab} & requests & separated fissile material\\
                      & offers & recycled MOX\\
\hline
\textbf{Separations} & requests & all spent fuel types \\
\Class{cycamore::Separations} & offers & separated fissile material\\
                      & efficiency & 0.99\\
                      & Pu separation capacity & $6.0E4$ [kg/month] \\
\hline
\textbf{Repository} & requests & all waste\\
\Class{cycamore::Sink} & capacity & $\infty$\\
\hline
\textbf{UOX Fabrication} & fffers & UOX\\
\Class{cycamore::Source} & capacity & $\infty$\\
\hline
\textbf{DU Source} & offers & depleted U\\
\Class{cycamore::Source} & capacity & $\infty$\\
\hline
\end{tabularx}
\caption{Facility Configurations for Example Simulations}
\label{tab:facconfigs}
\end{table}

@@

Modifying the input file specification to model each of the 3 fuel cycles was
done by making simple adjustments to the commodities and trade preferences for
each of the facilities.  The reactor was configured to request recycled \gls{MOX}
fuel with a higher preference than new \gls{UOX} fuel. For the No Recycle case,
the \Class{Reactor} was set to offer all spent fuel as waste.  For the 1-pass
recycle case, the \Class{Reactor} offered spent \gls{UOX} into a spent fuel market,
but spent \gls{MOX} is still offered as waste.  In the Infinite-Pass Recycle case,
the \Class{Reactor} offers all burned fuel into a spent fuel market. The
separations facility requests spent fuel with a higher preference than the
repository resulting in preferential recycle.  All these preferences are easy
to adjust and \Cyclus dynamically handles supply constraints and non-uniform
preference resolution.  It is notable that separations and recycle fuel
fabrication capacity are deployed identically in all simulations.  In the once
through case, the recycling loop never acquires material, and so reactors
always receive fresh \gls{UOX} fuel.  The \gls{DRE} ensures everything operates
smoothly in all cases.

>>>>

To illustrate the flexibility of \Cyclus, this section will discuss the 
creation and results of a range of representative fuel cycle simulations.
These examples are not the limit of \Cyclus' capabilities, which are extended with each new
addition to the ecosystem, as discussed above.  Rather, these simulations are
designed to illustrate that \Cyclus matches the capabilities of any
recipe-based simulator and that variations on a single \Cyclus simulations can 
be run with small changes to the input specification. For simplicity of the 
demonstration, many simplifying assumptions have been
made with respect to material compositions, fuel transmutation, among others.
The three fuel cycles examined are:

@@

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{|X|r|X|}
\hline
\textbf{Facility} &\textbf{Parameter} & \textbf{Value}\\
\hline
\textbf{LWR} & type & LWR\\
\Class{cycamore::Reactor} & batches & $3$ [batches/cycle]\\
                  & batch size & $20000$ [kg HM]\\
                  & cycle length & $18$ [months]\\
                  & refuelling time & $2$ [months]\\
                  & requests & recycled MOX (1st preference)\\
                  & requests & enriched UOX (2nd preference)\\
\hline
\textbf{Recycled Fuel Fabrication} & requests & depleted uranium\\
\Class{cycamore::Fab} & requests & separated fissile material\\
                      & offers & recycled MOX\\
\hline
\textbf{Separations} & requests & all spent fuel types \\
\Class{cycamore::Separations} & offers & separated fissile material\\
                      & efficiency & 0.99\\
                      & Pu separation capacity & $6.0E4$ [kg/month] \\
\hline
\textbf{Repository} & requests & all waste\\
\Class{cycamore::Sink} & capacity & $\infty$\\
\hline
\textbf{UOX Fabrication} & offers & UOX\\
\Class{cycamore::Source} & capacity & $\infty$\\
\hline
\textbf{DU Source} & offers & depleted U\\
\Class{cycamore::Source} & capacity & $\infty$\\
\hline
\end{tabularx}
\caption{Facility Configurations for Example Simulations}
\label{tab:facconfigs}
\end{table}

@@

To model each of the three fuel cycles, only simple 
adjustments to the input file specification were necessary. Specifically,  
only the commodity types and trade preferences for
each of the facilities needed to be altered from one simulation to another.

For all cases, the reactor was configured to request recycled \gls{MOX}
fuel with a higher preference than new \gls{UOX} fuel. For the No Recycle case,
the \Class{Reactor} was set to offer all spent fuel as waste.  For the 1-pass
recycle case, the \Class{Reactor} offered spent \gls{UOX} into a spent fuel market,
but spent \gls{MOX} is still offered as waste.  In the Infinite-Pass Recycle case,
the \Class{Reactor} offers all burned fuel into a spent fuel market. The
separations facility requests spent fuel with a higher preference than the
repository resulting in preferential recycle.  All these preferences are easy
to adjust and \Cyclus dynamically handles supply constraints and non-uniform
preference resolution.  It is notable that separations and recycle fuel
fabrication capacity are deployed identically in all simulations.  In the once
through case, the recycling loop never acquires material, and so reactors
always receive fresh \gls{UOX} fuel.  The \gls{DRE} ensures everything operates
smoothly in all cases.
